---
title: "Exercises for class 1"
output: html_document
date: "13-02-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rethinking)
```

# Exercises for Class 1

## Supporting code

Below is code from Chapter 2 of the book that you can use to do the exercises. Not all the code you require is here though. Make sure to not rush it and take time to play around with each function. :))

```{r}
# Grid Approximation

# define grid
p_grid = seq(from = 0, to = 1, length.out=20)

# define prior
prior = rep(1, 20)

# compute likelihood at each value in grid
likelihood = dbinom(6, size = 9, prob = p_grid)

# compute product of likelihood and prior
unstd.posterior = likelihood * prior

# standardize the posterior so it sums to 1
posterior = unstd.posterior / sum(unstd.posterior)

# plot the distribution
plot(p_grid, posterior, type = "b",
     xlab = "probability of water", ylab = "posterior_probability")
mtext("20 points")

```

## Exercises

### Easy

2E1. 

```{r}

# Your answer here.
# (2) Probability of rain given monday Pr(rain|Monday)

```

2E2.

```{r}

# Your answer here.
# (3) The probability of it being Monday given that it is raining

```

2E3.

```{r}

# Your answer here.
# (1) Pr(Monday|rain)

```

2E4.

```{r}

# Discuss in pairs/groups. Ask me for a hint if you feel like it.
# It means that when randomly marking a spot on the globe there is 70% change of the spot being marked is in water. In other words, 70 out of 100 times the marked spot will be water.

```

### Medium

2M1.

```{r}

# Write your code here.

# Define grid
p_grid = seq(from = 0, to = 1, length.out = 20)

# Define prior
prior = rep(1, 20)

# Compute likelihood for each part of the grid
likelihood = dbinom(5, size = 7, prob = p_grid)
# For (1) W,W,W change to:
## likelihood = dbinom(3, size = 3, prob = p_grid)
# For (2) W,W,W,L change to:
## likelihood = dbinom(3, size = 4, prob = p_grid)
# For (3) L,W,W,L,W,W,W change to:
## likelihood = dbinom(5, size = 7, prob = p_grid)

# Compute product of likelihood and prior
unstd.posterior = likelihood * prior

# Standardize the posterior so it sums to 1
posterior = unstd.posterior / sum(unstd.posterior)

# Plot the distribution
plot(p_grid, posterior, type = "b",
     xlab = "probability of water", ylab = "posterior_probability")
mtext("20 points")


```

2M2.

```{r}

# In the book, McElreath says that we can do much better than choosing a uniform prior for estimating the coverage of water. Is this what we are doing here? How does that impact our estimation?

```

2M3.

```{r}

# Use the Bayes formula!

```

For the exercises below, I highly suggest you to grab a piece of paper and try to solve the problems in a 'visual' way.

2M4.

```{r}

# Write your probability here.

```

2M5.

```{r}

# Write your probability here.

```

2M6.

```{r}

# Write your probability here.

```
